---
title: "Insurance Charges in the United States"
description: |
  A short description of the post.
author:
  - name: Mikaela Mazey
    url: https://example.com/norajones
date: 03-25-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(readr)
library(ggplot2)
library(dplyr)

insurance <- read_csv("~/Documents/seniorproject2.0/insurance.csv")
View(insurance)
```

##Medical Insurance Charges in the United States

Since I am from Canada, and we pay for our medical bills through taxes, I was curious to analyze the insurance charges in the United States. 
I created a few visualizations that shows the data in a comprehensive way. I found this dataset in Kaggle and can be found [here](https://www.kaggle.com/mirichoi0218/insurance). The dataset does not give reference to what years the data represents, but I still found the data insightful.

#Male Insurance Charges Vs Female Insurance Charges in USA
```{r}

charges <- insurance %>% 
  mutate(Charges = charges/1000) %>% 
  group_by(age, sex) %>% 
  summarise(sum_charges = sum(Charges))

#groupby age and sum up values
#check to see if it's 18 yr olds or 18 and younger
#make a line chart. color by sex. or geom point with geom_smooth
#or boxplot by age


p <-charges %>% 
  ggplot(aes(x=age, y= sum_charges)) + 
  geom_line(aes(color=sex)) +
  labs(title="Medical Insurance Charges in the USA", x="Age", y="Insurance Charges / 1000 (USD)")+
  theme_bw()
p + scale_color_discrete(name = "Sex", labels = c("Female", "Male"))
```

From this visualization, we can see the variation of insurances charges for both genders. We identify that there is a spike for medical insurance charges from the ages 18-20 for both genders. The insurance charges somewhat average out and then get higher at around the age of 45. This makes perfect sense: As people age, their insurance charges increase. I also found the initial spike interesting, but this also makes sense as young adults are more reckless with their actions. 

```{r}

p2 <-insurance %>% 
  ggplot(aes(x=sex, y=charges))+
  geom_boxplot(aes(color=sex))+
  theme(legend.position = "none")+
  labs(title= "Insurance Charges In The United States", x="Gender", y="Insurance Charges (USD)")+
  theme_bw()

p2 + scale_color_discrete(name = "Sex", labels = c("Female", "Male"))



```
I created this plot to see which gender has the higher medical insurance charges. After I created this boxplot, I realized how close they are when comparing the medians. However, we can see that males tend to have higher medical insurance bills when compared to females. 


```{r}

new_charges <- insurance %>% 
  mutate(new_charges = charges/1000000) %>% 
  group_by(region) %>% 
  summarise(sum_charges = sum(new_charges))

new_charges %>% 
  ggplot(aes(x=region, y=sum_charges))+
  geom_col(fill="bisque3")+
  labs(title="Insurance Charges for Various Regions in USA", x="Region", y="Insurance Charges/million (USD)")+
  theme_classic()


```
I then wanted to take a look at the different regions in the United States. I was curious to see if there was a specific region that had higher medical insurance costs. I wanted to compare between males and females and we can see that for both genders, the Southeast region has the highest insurance charges.



